Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-08-06 paper.tex
Minor corrections following Soudabeh's updates

\subsection{Varying the number of factors}
Figure~\ref{fig:factors} shows the effect of the number of factors used 
in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
clear effect of the number of factors on the accuracy. \todo{Soudabeh, add results for 50 and 800 factors}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
\caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
\label{fig:factors}
\end{figure}

@@

Figure~\ref{fig:error-locality} shows the results obtained by RFNU on 
the Freesurfer dataset for a training ratio of 0.6. The prediction 
error is localized (1) at the bottom of the matrix, which corresponds 
to the end of the execution, and (2) in the regions where file 
reproducibility varies across subjects, i.e., lines are not entirely 
black or entirely white.
\begin{figure}
\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
\label{fig:error-locality}
\end{figure}

>>>>

\subsection{Varying the number of factors}
Figure~\ref{fig:factors} shows the effect of the number of factors used 
in the ALS optimization for the RFNU method, and the synthetic dataset with 8 types. 
For training ratios greater or equal than 0.5, the accuracy obtained 
with 3 factors is substantially higher than with 2 factors. Beyond 
3, the number of factors does not have an effect on the accuracy. 
This shows that the data is best explained by 3 factors. For training 
ratios lower than 0.5, the number of factors does not have any effect 
on the accuracy, presumably due to the low accuracy of the method.\todo{Soudabeh, check if the factors can be interpreted.}

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
\caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
\label{fig:factors}
\end{figure}

\subsection{Varying the number of iterations}
Figure~\ref{fig:iterations} illustrates the effect of the number of 
iterations used in the ALS optimization, for the 
RFNU method, the synthetic dataset with 8 types, and 50 factors.

From a training ratio of 0.7, the number of iterations has a moderate 
effect on the accuracy. Our previous experiments used 5 iterations, 
which only degrades the accuracy slightly compared to 15 or 20 iterations.

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
\caption{Effect of the number of iterations used in ALS, RFNU method, 50 factors, synthetic dataset.}
\label{fig:iterations}
\end{figure}

@@

Figure~\ref{fig:error-locality} shows the results obtained by RFNU on 
the Freesurfer dataset for a training ratio of 0.6. The prediction 
error is localized (1) at the bottom of the matrix, which corresponds 
to the end of the execution, and (2) in the regions where file 
reproducibility varies across subjects, i.e., lines are not entirely 
black or entirely white.
\begin{figure}
\centering
\includegraphics[width=0.55\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
\label{fig:error-locality}
\end{figure}
